\section{Problem Based Learning} 
\label{PBL}

Problem Based Learning $(PBL)$ is a method to organize the group work which will help to approach the project's objectives. Collaboration in the group is a very important factor to get the project working as efficient and fluent as possible.
Therefore there has initially been put some work into a way to work and organize the project. By doing that in the beginning we will save important time later on.
First of all this is a group of 6 people so it is important to give different tasks to different people to keep it efficient. 

To make sure everyone know what is going on there will be a group meeting at least once a week but usually there will be more. Here the group members present their progress for each other, share the knowledge acquired and, if there has been any problems, it will be discussed here. In these meetings there will be one chair-person who needs to make sure that all the topics of the agenda are being discussed in detail. Besides the chair-person there will be a responsible for writing the minutes-of-meeting. 

A supervisor meeting will be held at least once every two weeks. Again with a chair-person and a responsible for writing. Before the meeting, the agenda and questions to be discussed are sent to the supervisors and afterwards the group will sent the minutes-of-meeting. The goal here is to show the supervisors that the project is moving in the right direction and to get the questions answered. Furthermore, the group sends the documentation progress to get feedback regularly.

To organize the tasks between the group members the web page \textit{Trello} is used as a taskboard. All the tasks that should be done are written here and divided in sections: "To do", "Doing" and "Done". This makes sure that everybody can see which tasks are in progress and who is working on them. A time-plan has been develop for the "P0" and the "P1" report using a Gantt chart (Figure \ref{gantt}), so there is a common agreement on which tasks should be done at first and the milestones of the project report.              
