\section{PCB building} \label{sec:pcb_building}
The building of the PCB in iteration one of the development has been done according to the test described in the following section. It has been divided into smaller tests, to validate that every part of the system works properly. The first part is the test of the control part, so the optocouplers, drivers and sensors \todo{But the first test here is power supplies and you don't mention them. Stef}. The last part is then the test of the power stage of the converter \todo{This is section 6.2 isn't it? maybe say that in the next section is this test because it seems like it's going to be done in this section. Stef}. It has been chosen only to solder the buck leg of the converter to validate the design, and discover faults which must be dealt with in iteration two. Before starting the test all vias, capacitors and test-points are soldered to assure connectivity.

\subsection{Power supplies} \label{sec:test_pwr_sup}
The purpose of the first test was to validate the different power supplies in the converter. For this test it is necessary to solder the in-TRACO and the $5V$ voltage regulator. The three LEDs and the resistors should also be soldered. Apply $5V$ at connector J4 and $12V$ at connector J2. The test is conducted by following table \ref{tab:test_pwr_sup}

\begin{table}[H]
	\centering
	\begin{tabular}{|>{\centering}p{1cm}|p{5.3cm}|p{4cm}|>{\centering}p{2cm}|}
		\hline
		\rowcolor{lightgray}\multicolumn{4}{|l|}{ \textbf{Test of power supplies}} \\ \hline
		\rowcolor{lightgray} \textbf{ID} & \textbf{Test} & \textbf{Test-points} & \textbf{Pass/Fail} \tabularnewline \hline
		1.1 & All LEDs must be lit & DS1-2-4 & Pass  \tabularnewline \hline
		1.2 & Measure $5V$ at low-voltage & 5V-LV \& GND-LV & Pass \tabularnewline \hline
		1.3 & Measure $12V$ at high voltage, low-side & 12V \& GND-in & Pass  \tabularnewline \hline
		1.4 & Measure $12V$ at output of in-TRACO & 12V-in \& L-in & Pass  \tabularnewline \hline
		1.5 & Measure $5V$ at the output of the voltage regulator & 5V-HV \& GND-sen & Pass  \tabularnewline \hline
	\end{tabular}
	\caption{Test of power supplies.}
	\label{tab:test_pwr_sup}
\end{table}

\subsection{Optocouplers} \label{sec:test_opto}
The second part of the test is to validate the optocouplers. This includes that the output of the optocoupler should follow the input. For this test it is necessary to solder opto1-2, and an extra test-point at the output of the two optocouplers. Because of a wrongly chosen optocoupler with a supply voltage at $5V$, a voltage divider must be added. This will be placed between the supply pins of the IC, and will divide $12V$ into $5V$. Start the test by applying $5V$ at connector J4, $12V$ at connector J2 and a $5V-50kHz$ square waveform with $50\%$ duty-cycle at PWM1-2. 

\begin{table}[H]
	\centering
	\begin{tabular}{|>{\centering}p{1cm}|p{5.3cm}|p{4cm}|>{\centering}p{2cm}|}
		\hline
		\rowcolor{lightgray}\multicolumn{4}{|l|}{ \textbf{Test of optocouplers}} \\ \hline
		\rowcolor{lightgray} \textbf{ID} & \textbf{Test} & \textbf{Test-points} & \textbf{Pass/Fail} \tabularnewline \hline
		2.1 & Measure $5V$ at the supply of opto1-2 & IC pin 6(+) \& 4(-) & Pass  \tabularnewline \hline
		2.2 & Measure $5V-50kHz$ at the input of optocoupler 1 & TST1 \& GND-LV & Pass \tabularnewline \hline
		2.3 & Measure $5V-50kHz$ at the output of optocoupler 1 & Opto1-out \& L-in & Pass  \tabularnewline \hline
		2.4 & Measure $5V-50kHz$ at the input of optocoupler 2 & TST2 \& GND-LV & Pass  \tabularnewline \hline
		2.5 & Measure $5V-50kHz$ at the output of optocoupler 2 & Opto2-out \& GND-in & Pass  \tabularnewline \hline
	\end{tabular}
	\caption{Test of the optocouplers.}
	\label{tab:test_opto}
\end{table}

\subsection{Drivers} \label{sec:test_drivers}
The next part of the test consist of the drivers. For this it is necessary to solder drv1-2, M1-2 and the resistors R5-R10. The input threshold of the drivers is defined as $V_{DD}-3.1V$. Because of the $5V$ optocouplers, the supply voltage of the drivers must be lowered to $5V$, for the switching to work. A consequence of this is that the voltage divider that supplies the optocoupler should be removed. Start the test by applying $5V$ at connector J2 \& J4 and a $5V-50kHz$ square waveform with $50\%$ duty-cycle at PWM1-2. The test is conducted by following table \ref{tab:test_drivers}.

\begin{table}[H]
	\centering
	\begin{tabular}{|>{\centering}p{1cm}|p{5.3cm}|p{4cm}|>{\centering}p{2cm}|}
		\hline
		\rowcolor{lightgray}\multicolumn{4}{|l|}{ \textbf{Test of drivers}} \\ \hline
		\rowcolor{lightgray} \textbf{ID} & \textbf{Test} & \textbf{Test-points} & \textbf{Pass/Fail} \tabularnewline \hline
		3.1 & Measure $5V$ at the supply of the drivers & IC pin 6-7(+) \& 2-3(-) & Pass  \tabularnewline \hline
		3.2 & Measure $5V-50kHz$ at the output of driver 1 & PWM1 \& L-in & Pass \tabularnewline \hline
		3.3 & Measure $5V-50kHz$ at the output of driver 2 & PWM2 \& GND-in & Pass  \tabularnewline \hline
	\end{tabular}
	\caption{Test of the drivers.}
	\label{tab:test_drivers}
\end{table}

\subsection{Sensors} \label{sec:test_sensors}
The last part of the control system test consist of the sensor circuits. For this test it's necessary to solder the input voltage sensor U2, the current sensor and the operational amplifier. Furthermore the resistors $R_{17}-R_{22}+R_{25}+R_{32}+R_{33}$ and capacitors $C_{17}+C_{22}$ should be soldered. Before testing a jumper should be placed between J5-2 and J5-3, to select the bandwidth of the current sensor to $80kHz$. The inductor, M1 and M3 should also be shorted to achieve a current flow through the current sensor. 

Attach a load resistor at $100\Omega$. With an input voltage at $10V$, this should correspond to a output current at $100mA$. Because of the differential offset in the current sensor, this should be equal to $2.6V$. After test 4.3, raise the input voltage to $20V$ for validation of linearity in the sensors.

\begin{table}[H]
	\centering
	\begin{tabular}{|>{\centering}p{1cm}|p{5cm}|p{4.3cm}|>{\centering}p{2cm}|}
		\hline
		\rowcolor{lightgray}\multicolumn{4}{|l|}{ \textbf{Test of sensors}} \\ \hline
		\rowcolor{lightgray} \textbf{ID} & \textbf{Test} & \textbf{Test-points} & \textbf{Pass/Fail} \tabularnewline \hline
		4.1 & Measure $10V$ at the input of the converter & Vin \& GND-in & Pass  \tabularnewline \hline
		4.2 & Measure $1V$ at the output of the voltage sensor & Vi-sen \& GND-sen & Pass \tabularnewline \hline
		4.3 & Measure $2.6V$ at the output of the current sensor & IL-sen-Raw \& GND-sen & Pass  \tabularnewline \hline
		4.4 & Measure $20V$ at the input of the converter & Vin \& GND-in & Pass  \tabularnewline \hline
		4.5 & Measure $2V$ at the output of the voltage sensor & Vi-sen \& GND-sen & Pass \tabularnewline \hline
		4.6 & Measure $2.7V$ at the output of the current sensor & IL-sen-Raw \& GND-sen & Pass  \tabularnewline \hline
	\end{tabular}
	\caption{Test of the sensors.}
	\label{tab:test_sensors}
\end{table}






 

