%%% Chapter 7 - Test and validation of results %%%

\chapter{Experimental results} \label{ch:test_validation}

When the design stage is completed, the system must be tested in the PV laboratory available at Aalborg University. The system design consisted of hardware and control design. The experimental results will show whether the system is compliant with the initial goals. The system test is performed in two steps: first the hardware design is tested without the MPPT controller and, after this step is completed, the complete system will be tested to show the real performance of the MPPT unit.

The hardware design testing is performed following an incremental fashion. The components are individually soldered to the PCB and tested. The tests are short and with clear boundaries. These features ease the errors' finding and troubleshooting. This procedure validates the proper behaviour in the single component but also lets analyse the effect of additional components. The assembly and test procedure will be defined prior to the PCB assembly. The test and its expected results are clear before starting. When the PCB is assembled and all the integration tests are passed, the complete converter is tested. This system test is performed by running the converter with a fixed duty cycle. This test allows the validation of the converter design, including voltage and current ripples, thermal test, gain and power losses.

The control design testing must demonstrate that the control signals are properly calculated in order to achieve maximum power generation. These signals are received by the previously tested hardware implementation. The testing consists on black box testing where only a few internal parameters are monitored through the controller's console. The 
system's stability and dynamic behaviour will be analyzed.

%% Section decribing the PCB building of the first iteration %%
\input{docs/test/pcb_building1.tex}

\input{docs/test/MPPT.tex}