---
title: "Exam 2"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

Remember to load the `mosaic` package first:
```{r message=FALSE}
library(mosaic)
```

## Part I: Directed reading activities

An educator conducted an experiment to test whether new directed reading
activities in the classroom will help elementary school pupils improve
some aspects of their reading ability.

She arranged for a third grade class of 21 students to follow these activities for an 8-week period. A control classroom of 23 third graders followed the same curriculum without the activities. At the end of the 8 weeks, all students took a Degree of Reading Power (DRP) test, which measures the aspects of reading ability that the treatment is designed to improve.


Read in the data:
```{r}
reading <- read.table("http://asta.math.aau.dk/dan/static/datasets?file=reading.dat", header=TRUE)
head(reading)
```

**Use a boxplot to compare the of measurements** of `DRP` for `Treated`(direct reading activities) and `Control` visually.

*we want to see the score of each group, DRP=the experiment they have done*
```{r}
bwplot(Response ~ Treatment , data = reading)
```

*As it can be seen in the boxplots, the response dispersion for the Treated students is more narrow than the one for Control students, which states that there are not very extreme values between the treated students. Also, we can state that the treated students in overall have a higher grade (the mean value and the median is slightly higher for the Treated students) = so in overall the treated ones are better trained for a reading exam than the non treated ones.Although there are some non treated students that have higher marks than the treated ones. There are not outliers in any sample*

Use `favstats` to **make a numerical summary of the measurements** for `Treated` and `Control`.

```{r}
favstats(Response ~ Treatment, data = reading)
```

*The summary results are in concordance with the boxplots. The mean for the Treated students is higher, whereas the standard deviation is lower.*

### Working with Treated students

-   **Write down a point estimate of the mean** of DRP for students
    following the new *directed reading activities* and explain how this
    is calculated.
    
*The point estimate of the mean for Treated students is the mean of the partial sample of those students. The same approximation is done for the Control Students.*

$$\overline y_{Treated} = \frac{1}{n_1} \sum\limits_{i=1}^{n_1}{y_i} \quad \text{, where } y_i \text { are the values for the Treated group} $$

```{r, echo = FALSE}
Control <- subset(reading, Treatment == "Control")
Treated <- subset(reading, Treatment == "Treated")
y1 = mean(~ Response, data = Control)
y2 = mean(~ Response, data = Treated)
y2
```


-   **Write down a point estimate of the standard deviation** of DRP for
    this group and explain how this is calculated.
    
*The point estimate of the standard deviation for Treated students is the standard deviation of the partial sample of those students. The same approximation is done for the Control Students. *

$$s = \sqrt{\frac{\sum\limits_{i=1}^{n_1}{(y_i-\overline y_T)^2}}{n_1-1}}$$
*The -1 in the denominator is due to the Bessel correction. *

```{r }
n1 = 23
n2 = 21
s1 = sd(~ Response, data = Control)
s2 = sd(~ Response, data = Treated)
s1
s2
```

*Also, the standard error is aproximated by the next formula* $$se = \frac{\sigma}{\sqrt n}$$

```{r}
se2 = s2/sqrt(n2)
se2
```

-   Write down a **95% confidence interval for the mean** of DRP for this
    group and explain how this is calculated.
    
*The 95% confidence interval for the Treated group is defined as follows: * $(a,b) = \overline y \pm t(se)$

*we use t score because the number of samples is less than 30*

```{r}
t<-qdist("t", p = 0.025, df = 21-1)
t
y2+c(t*se2,-t*se2)
```

*All those results can be obtained by the comand* `t.test`

```{r}
t.test( ~Response, data = Treated, conf.level = 0.95)
```

*We can say with a 95% of confidence level that if we take antoher sample the mean will be aroun that interval (46.46-56.48)*


### Comparing Treated and Control students

Use the **command `t.test` to compare the mean DRP of the two groups**.

```{r}
t.test(Response ~ Treatment , data = reading)
```

Go through the details of the output from t.test.

-   What the relevant **null hypothesis** and the corresponding **alternative hypothesis** is.
    
*The null hypothesis is* $H_0:\hat\mu_1=\hat\mu_2$ *and the alternative hypothesis is * $H_a:\hat\mu_1\neq\hat\mu_2$

*We can reject the 0 Hypothesis as the pvalue is less than 5%. The means are not equal!*

-   Choice and **calculation of test statistic**.

*First, is neccesary to calculate the standartd error of the sample difference, as follows:*

$se_d=\sqrt{\frac{s_1^2}{n_1}+\frac{s_2^2}{n_2}}$

```{r, echo=FALSE}
sed = sqrt(s1^2/n1+s2^2/n2)
sed
```

*The value of t for the t.test is calculated as follows:* $t=\frac{\overline y_2-\overline y_1}{se_d}$

```{r }
y1
y2
t = (y1-y2)/sed
t
```


-   **Calculation of p-value** and its interpretation in connection to a
    conclusion of the analysis.
    
*Once obtained the t value, the probability of occurrence of this value is obtained by the t curve. The p-value is defined as the left probability of this value times two.*   


```{r }
P = 2*pdist("t", q = t, df = 37.855)
P
```
When the p-value is small, we can consider that we can reject the* $H_0$ *hypothesis.

-   **Calculation** and interpretation of a relevant **confidence interval**.

*The confidence interval represents the range in between the difference of means is, with some certainty. It is calculated by the t value, the difference of means and the standard error, as follows:* $$(a,b) = (\bar y_2-\bar y_1)\pm t(se_d)$$

$$(a,b) = (41.52-51.47)\pm 2(4.3)$$

*First, we have to calculate the t value, with a 95% confidence.*

```{r, echo = FALSE}
t2 <- qdist("t", p = 0.025, df = 37.855)
t2
```

*Then, we calculate the confidence interval (95%).*

```{r, echo = FALSE}
d = y1-y2
d+c(t2*sed,-t2*sed)
```


## Part II: Determining sample size

Estimate the proportion of danish companies with less than 10
employees determine the necessary sample size for the estimate to be
accurate to within 0.06 with probability 0.90. Based on results from a
previous study in 2013, we expect the proportion to be about 0.70.

*The margin of error when estimating a proportion is*

$M = z \sqrt {\frac{\pi(1-\pi)}{n}}$

*Solving the equation for obtaining n*

$n = \pi(1-\pi)(\frac{z}{M})^2$

*With the given values, the sample size can be calculated*

```{r }
M <- 0.06
pi <- 0.7
z<-qdist("norm", p= 0.05, mean = 0, sd = 1)
z
n <- pi*(1-pi)*(z/M)^2
n
```




```{r, echo=FALSE}


M = 0.06
pi = 0.5
z<-qdist("norm", p= 0.05, mean = 0, sd = 1, plot = FALSE) 
n = pi*(1-pi)*(z/M)^2

```










